Nested sampling with two objective functions

### 2015-11-03 Paper/ms.tex
Better temperature choice to show the canonical dist
Updated scalars

We tested the algorithm on a simple 100-dimensional example, where the
prior is a uniform distribution between 0 and 1 for each coordinate:
\begin{eqnarray}
\pi(\xx) &=& \prod_{i=1}^{100}
\left\{
\begin{array}{lr}
1, & x_i \in [0, 1]\\
0, & \textnormal{otherwise.}
\end{array}
\right.
\end{eqnarray}
The two objective functions are:
\begin{eqnarray}
L_1(\xx) &=& -\sum_{i=1}^{100} \left(x_i - 0.5\right)^2\\
L_2(\xx) &=& -\sum_{i=1}^{100} \log\left[1 +
\left(\frac{x_i - 0.5}{0.01}\right)^2
\right].
\end{eqnarray}
The canonical distribution at low temperature for $L_1$ and high temperature
for $L_2$ is a gaussian centered at 0.5 with standard deviation
$\sqrt{T_1/2}$. At high temperatures for $L_2$ and low temperatures for $L_1$ the
canonical distributions are Cauchy centered at 0.5 with width
$0.01\sqrt{T_2}$.

@@

\begin{figure}
\centering
\includegraphics[scale=0.75]{figures/output.png}
\caption{\label{fig:output}}
\end{figure}

>>>>

We tested the algorithm on a simple 100-dimensional example, where the
prior is a uniform distribution between 0 and 1 for each coordinate:
\begin{eqnarray}
\pi(\xx) &=& \prod_{i=1}^{100}
\left\{
\begin{array}{lr}
1, & x_i \in [0, 1]\\
0, & \textnormal{otherwise.}
\end{array}
\right.
\end{eqnarray}
The two objective functions are:
\begin{eqnarray}
L_1(\xx) &=& -\frac{1}{2}\sum_{i=1}^{100} \left(\frac{x_i - 0.5}{0.01}\right)^2\\
L_2(\xx) &=& -\sum_{i=1}^{100} \log\left[1 +
\left(\frac{x_i - 0.5}{0.01}\right)^2
\right].
\end{eqnarray}
The canonical distribution at low temperature for $L_1$ and high temperature
for $L_2$ is a gaussian centered at 0.5 with standard deviation
$0.01\sqrt{T_1}$. At high temperatures for $L_2$ and low temperatures for $L_1$ the
canonical distributions are Cauchy centered at 0.5 with width
$0.01\sqrt{T_2}$.

@@

\begin{figure}
\centering
\includegraphics[scale=0.75]{figures/output.png}
\caption{The sequence of discarded particles (yellow) and
points representing the canonical distribution at temperatures
$(T_1, T_2) = (200, 100)$ (black).\label{fig:output}}
\end{figure}
